Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-10 Latex/tex/pr.tex
paper prepare abstract

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

@@

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

@@

\rho_{u(v,i)} =  \frac{P_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}}

@@

Where, $P_{u(v,i)}$ represents the transmitted power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 

@@

$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks(PRB) to UE.

@@

It is assumed that interference signal applied from UEs with same PRB.

@@

Let, the required resources for VNF $f$ in slice $s$ is represented by

@@

\Omega_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \}

@@

Where, $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU.
Also, in the Core Network(CN), there are $N_{D}$ data centers(DC), which served VNFs. Each DC contains several servers that supply VNF's needs.

@@

@@

\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{R_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_{r_{tot}}(\boldsymbol{P},\boldsymbol{A})},

@@

Assume the power consumption of baseband processing at each data center that is mapped to VMs of a slice is depicted as

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{Y})} \\

@@

&D_{s} \leq D_{s}^{th}  &&\quad \forall s,\label{c15} \\

@@

& \sum_{f=1}^{F_s}\Omega_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                      
 && \quad \forall f, \forall s  \label{c22}

@@

The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem. The First and main problem is

@@

&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i, \\
&D_{s} \leq D_{s}^{th}  &&\quad \forall s

@@

and the second problem is 

@@

& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s, \\
& \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
& \sum_{f=1}^{F_s}\Omega_{(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_d                       && \quad \forall f, \forall s 

@@

\subsection{Proposed Method For Problem \eqref{constraints1}}

@@

\subsubsection{First Sub-Problem}

@@

\For {$ 1\leq i \leq  S$}
\For {$ 1\leq j \leq  V$}

@@

\subsubsection{Second Sub-Problem}

@@

&\max \limits_{\boldsymbol{P}} (R_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=\\
& R_{total}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.

@@

This subproblem can  be solved using Lagrangian function and iterative algorithm. 
Since, Interference is a function of power of UEs, for simplicity, we assume an upper bound for interference (the worst-case) as follow
 \bar{I}_{u_{(v,i)}} &= 
 \underbrace{\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{\substack{l=1 \\ l\neq i}}^{{U}_v} \gamma_{1}  p_{max} a_{vs}\zeta_{u_(v,i),n,s}\zeta_{u_(v,l),n,s}}_{\text{(intra-service interference)}}\\
&+ \underbrace{\sum_{\substack{y=1 \\ l\neq v}}^{V}\sum_{s=1}^{S}\sum_{n=1}^{N_s}\sum_{l=1}^{{U}_y} \gamma_{2}  p_{max}   a_{ys} \zeta_{u_(v,i),n,s}\zeta_{u_(y,l),n,s}}_{\text{(inter-service interference)}}\\
and $\gamma_{2} =|\boldsymbol{h}_{\mathcal{R}_s, u_{(v,i)}}^H \boldsymbol{w}_{\mathcal{R}_{s},u_{(y,l)}}|^2$.\newline

@@

@@

&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (C_{r_{(s,i)}}-C_{r_{(s,i)}}^{max}).\\ 
&- \sum\limits_{s=1}^{S}  \kappa_{r_{(s,i)}} (D_{s}-D_{s}^{max}).\\ 

@@

@@

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

@@

\begin{abstract}
Many major telecommunication companies confirmed the unification of the xRAN Group with the C-RAN Alliance to establish a global 'carrier-led' effort to bring greater transparency of Open-RAN 
(O-RAN), to the next-generation of radio access network. \newline
To increase energy efficiency and optimize allocation of resources, Network Slicing (NS) is considered as a best method in 5G in order to virtualize the common physical network into several logical end-to-end networks. Every slice consists of a part of core network resources, network functions, and radio access network resources as a functional end-to end network. \newline
In this paper, we elaborates joint NS in RAN and Core of O-RAN system and investigate optimal power 
of each User Equipment (UE) to jointly maximize Energy Efficiency and minimize consumption power of physical resources in a downlink channel. The problem is formulated as a mixed integer optimization problem that can be decompose into two independent sub-problems for RAN and Core. 
Heuristic algorithms is proposed to each of sub-problems to solved the first sub-problem in order to simultaneously map slices to services and optimize power and the second sub-problem in order to map slices to physical resources and minimize number of active Data Centers (DC).
\end{abstract}

\begin{IEEEkeywords}
O-RAN, Network Slicing, Energy Efficiency, Data Center
\end{IEEEkeywords}

\section{Introduction}

@@

\rho_{u(v,i)} =  \frac{p_{u(v,i)}\sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}}{BN_0 + I_{u(v,i)}}

@@

Where, $p_{u(v,i)}$ represents the transmitted power allocated by RRHs to $i^{th}$ UE in $v^{th}$ service. Also, 

@@

$\zeta_{u(v,i),k,s} \in \{0,1\}$ is a binary parameter that map Physical Resource Blocks (PRB) to UE.

@@

It is assumed that interference signal for each UE, is applied from UEs which are using same PRB.
If we replace $p_{u_{(v,l)}}$ and $p_{u_{(y,l)}}$ by $P_{max}$, an upper bound $\bar{I}_{u_{(v,i)}}$ is obtained for $I_{u_{(v,i)}}$. Therefore, $\bar{\mathcal{R}}_{u_{(v,i)}} \forall v , \forall i$ is derived by using $\bar{I}_{u_{(v,i)}}$ instead of $I_{u_{(v,i)}}$ in equation \eqref{eq1} and \eqref{eq2}.\newline

@@

Let, the required resources for VNF $f$ in slice $s$ is represented by a three dimensional vector as follow

@@

\bar{\Omega}_{(f,s)} = \{\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}} \}

@@

Where,$\bar{\Omega}_{(f,s)}\in \mathbb{C}^{3}$ and $\Omega_{R_{f,s}}, \Omega_{M_{f,s}}, \Omega_{C_{f,s}}$ indicate the amount of required RAM, Memory and CPU.
Moreover total amount of required RAM, Memory and CPU of all VNFs in a slice is a three dimension vector which is defined as
\bar{\Omega}_{s}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{(f,s)}
Where, $F_s = M_{s_1} + M_{s_2}$ is the total number of VNFs in slice $s$.
\newline
Also, in the Core Network (CN), there are $N_{D}$ data centers(DC), which served VNFs. Each DC contains several servers that supply VNF's needs.

@@

Also we define a weighted parameter of $\tau_j$ as follow
\begin{equation}\label{wt}
\hat{\Omega}_{s}^{tot} &= w_R \bar{\Omega}_{R_s}^{tot} + w_M \bar{\Omega}_{M_s}^{tot} + w_C \bar{\Omega}_{C_s}^{tot} \\
\hat{\tau}_j &= w_R \tau_{R_{j}} + w_M \tau_{M_{j}} + w_C \tau_{C_{j}}
Where, $\boldsymbol{w} = \{w_R, w_M, w_C\}$ are the weight of RAM, Memory and CPU.

@@

\eta(\boldsymbol{P},\boldsymbol{A}) := \frac{\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{{U}_v}\mathcal{R}_{u_{(v,k)}} }{\sum\limits_{s=1}^{S} \sum\limits_{i=1}^{{R}_s}\bar{p}_{r_{(s,i)}}} = \frac{\mathfrak{R}_{tot}(\boldsymbol{P},\boldsymbol{A})}{P_{r_{tot}}(\boldsymbol{P},\boldsymbol{A})},

@@

Assume the power consumption of baseband processing at each data center that is mapped to VNFs of a slice is depicted as

@@

\max\limits_{\boldsymbol{P}, \boldsymbol{A}, \boldsymbol{Y} }   \quad &   \eta(\boldsymbol{P},\boldsymbol{A})+\frac{1}{\phi_{tot}(\boldsymbol{Y})} \\

@@

&D_{s} \leq D_{s}^{max}  &&\quad \forall s,\label{c15} \\

@@

& \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
 && \quad \forall \mathfrak{z}, \forall s  \label{c22}

@@

The main optimizaiton problem which is formulated as \eqref{constraints} can be decomposed into two independent optimization problem A and B. The problem A is introduced as bellow

@@

&C_{r_{(s,i)}} \leq C_{r_{(s,i)}}^{max}  &&\quad \forall s, \forall i,\label{cc14} \\
&D_{s} \leq D_{s}^{max}  &&\quad \forall s, \label{cc15} \\
& \sum_{s=1}^{S}a_{vs} \geq 1 &&\quad \forall s

@@

and the problem B is 

@@

\text{subject to} \quad & \sum_{d=1}^{D_c}\sum_{v=1}^{V}y_{s,d}a_{vs} \geq 1\times\sum_{v=1}^{V}a_{vs} &&\quad \forall s, \\
&  \bar{\Omega}_{\mathfrak{z}(s)}^{tot} = \sum_{f=1}^{F_s}\bar{\Omega}_{\mathfrak{z}(f,s)} \leq  \sum_{d=1}^{D_c} y_{s,d} \tau_{\mathfrak{z}_d}                      
 && \quad \forall \mathfrak{z}, \forall s\label{eqomega}

@@

\section{Proposed Method For Problem \eqref{constraints1}}

@@

\subsection{First Part of Sub-Problem A}\label{firstsub}

@@

\For {$i \gets 1$ to $S$}
\For {$j \gets 1$ to $V$}

@@

\subsection{Second Part of Sub-Problem A}\label{secondsub}

@@

&\max \limits_{\boldsymbol{P}} (\mathfrak{R}_{tot}(\boldsymbol{P}) - \eta^* P_{r_{tot}}(\boldsymbol{P}))=\\
& \mathfrak{R}_{tot}(\boldsymbol{P}^*) - \eta^* P_{r_{tot}}(\boldsymbol{P}^*) =0.

@@

\begin{proof}
See Appendix A
\end{proof}
The second subproblem can  be solved using Lagrangian function and iterative algorithm. 
Since, Interference is a function of power of UEs, for simplicity, we assume an upper bound $\bar{I}_{u_{(v,i)}}$ for interference (the worst-case). 
In order to make equation \eqref{constraints1} as a standard form of convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15}.

@@

\begin{equation}\label{lagrang}

@@

&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,j)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\ 
&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{vs}.\\ 

@@

Where,$\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Also, $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$ and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers which have non-zero positive elements. Optimal power is obtained from equation \eqref{lagrang} as follow
p_{u(v,i)}^{*} = \frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }
where, $\mathfrak{y}_{u(v,i)}= (-\mu_{u(v,i)}+\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and 
$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{N_s}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{vs}$. Also 
$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} (\xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$. 
By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained. 

@@

\subsection{Solving two part of Sub-problem A iteratively}
In \eqref{firstsub} and \eqref{secondsub} the details of solving each part of subproblem is depicted. 
Here, the algorithm of solving sub-problem A is shown in \textbf{Algorithm} \eqref{alg2}
\caption{Joint Network Slicing and Power Allocation}\label{alg2}
\State Set the maximum number of iterations $I_{max}$, convergence condition $\epsilon_{\eta}$  and the initial value $\eta^{(1)} = 0$
\State Set $\boldsymbol{P} = \boldsymbol{P}_{max}$
\For {$counter \gets 1$ to $I_{max}$}
\State Achieve $\boldsymbol{A}$ by applying Algorithm \eqref{alg}
\State Obtain $\boldsymbol{P}$ by using sub-gradient method which is mentioned in \eqref{secondsub}.
\If {$ \mathfrak{R}_{tot}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) - \eta^{(i)} P_{r_{tot}}(\boldsymbol{P}^{(i)},\boldsymbol{A}^{(i)}) < \epsilon_{\eta} $} 
\State Set $\boldsymbol{P}^*= \boldsymbol{P}^{(i)} $, $\boldsymbol{A}^*= \boldsymbol{A}^{(i)} $   and  $ \eta^{*} =\eta^{(i)} $;
\State break;
\State $i= i+1$, Setting $\boldsymbol{P} = \boldsymbol{P}^{(i)}$ ;
\subsection{Sub-Problem B}
In this subsection, we want to solve equation \eqref{constraints2} which is the placement of virtual resources to physical resource in order to minimize the number of using DCs. 
To achieve optimum $\boldsymbol{Y}$ heuristic algorithm and Mosek is applied. The details of heuristic algorithm is written in \textbf{Algorithm} \eqref{alg3}. In this algorithm, if a slice does not admit to a specific DC, it is remain for next placement. In next placement the residual slices, map to more than one DC according to their requirements.
\caption{Plecement of Physical resources into Virtual resources}\label{alg3}
\State Sort Slices according to $\hat{\Omega}_{s}^{tot} , \forall s$ in descending order.
\State Sort DCs according to $\hat{\tau}_j , \forall j$ in descending order. 
\State $\boldsymbol{Y} = \boldsymbol{0}$
\For {$d \gets 1$ to $D_c$}
\For {$s \gets 1$ to $S$}
\If {$\sum_{d=1}^{D_c}y_{s,d}==0$ and $\bar{\Omega}_{\mathfrak{z}(s)}^{tot} \leq \tau_{\mathfrak{z}_j} \forall \mathfrak{z}, \forall s$  } 
\State Set $y_{s,d} = 1$;
\State {$\tau_j$ $\gets$ {$\tau_j - \bar{\Omega}_{s}^{tot}$}}
\State  $\{ind_{residual} = s|({\sum_{d=1}^{D_c}y_{s,d}==0})\}$
\State Sort residual amount of DCs same as before in descending order.
\State Sort residual slices same as before in descending order.
\For {$r \gets 1$ to $S_{residual}$}
\For {$n \gets 1$ to $D_c$}
\State Set $y_{s,d} = 1$;
\State {$\bar{\Omega}_{s}^{tot}$ $\gets$ {$\bar{\Omega}_{s}^{tot}- \tau_j$}}
\If {$\bar{\Omega}_{s}^{tot}==0$}
\State Set $y_{s,d} = 1$;
\State {$\tau_j$ $\gets$ {$\tau_j - \bar{\Omega}_{s}^{tot}$}}
\State {break inner loop}
\section{Simulation}
In this section, Simulation and numerical results for the main problem are depicted.
